Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Tidied all the diagnoses into one column and their corresponding positive diagnosis into another by sample

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('depressive_disorders', 'anxiety_disorders', key = "Diagnosis", value = positive_n)

>>>>

dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)

head(dat.retro_positive_diagnosis_by_sample, 9)
